A Cost-based Approach for Fast Intrusion Detection

### 2017-06-05 tex/paper_v1.tex
add false alarm

As observed, the false alarm rates decay as the increasing level of features.

@@

\hline 
Methods/Features & Over all & TCP finger & UDP domain\_u & ICMP eco\_i \tabularnewline
\hline
\textbf{Level 1 Features} \tabularnewline
SVM & $3.86\%$ & $0.00\%$ & $0.67\%$ & $57.69\%$ \tabularnewline
Ours & $4.40\%$ & $99.26\%$ & $99.33\%$ & $94.27\%$\tabularnewline
\hline

@@

SVM & $81.39\%$ & $0.00\%$ & $0.45\%$ & $57.69\%$\tabularnewline
Ours & $3.49\%$ & $99.26\%$ & $99.78\%$ & $94.27\%$\tabularnewline
\hline

@@

SVM & $2.19\%$ & $0.00\%$ & $0.00\%$ & $19.23\%$\tabularnewline
Ours & $6.64\%$ & $99.26\%$ & $99.78\%$ & $98.89\%$\tabularnewline
\hline
\end{tabular}
\end{table*}

>>>>

As observed, the false alarm rates tends to decay as the increasing level of features. Especially, for the ICMP eco\_i models, the false alarm rates decay significantly for Level 3 features. For these type of situations, the extraction of high level features is necessary.

@@

\hline 
Methods/Features & Over all & TCP finger & UDP domain\_u & ICMP eco\_i \tabularnewline
\hline
\textbf{Level 1 Features} \tabularnewline
SVM & $3.86\%$ & $0.00\%$ & $0.67\%$ & $57.69\%$ \tabularnewline
Ours & $4.40\%$ & $0.00\%$ & $0.67\%$ & $57.69\%$\tabularnewline
\hline

@@

SVM & $1.81\%$ & $0.00\%$ & $0.45\%$ & $57.69\%$\tabularnewline
Ours & $3.49\%$ & $0.00\%$ & $0.45\%$ & $57.69\%$\tabularnewline
\hline

@@

SVM & $2.19\%$ & $0.00\%$ & $0.00\%$ & $19.23\%$\tabularnewline
Ours & $6.64\%$ & $0.00\%$ & $0.00\%$ & $7.69\%$\tabularnewline
\hline
\end{tabular}
\end{table*}
